Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-21 paper/ijcai/paper.tex
pass on background

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium}
(Accessed on \today)}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in
number of lines---of chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available at \textit{$<$anonymized for double-blind review$>$}.

@@

\begin{wrapfigure}[8]{2}{0.3\textwidth}
  \hspace{-2ex}
  \centering
  \scriptsize
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}

@@

Conceptually, if the oracles implemented in faulty tests are too
general, the critical slicing algorithm could produce slices without
the faulty code. For example, consider the scenario of an unexpected
Null-Pointer Exception (NPE) thrown in the code. If the oracle checks
for the presence of NPE regardless of where it occurs, it is possible,
in principle, that the final slice does not include the faulty code
but still raises NPE (in a different part of the code). The critical
slicing algorithm would consider that as an acceptable simplification
and would continue. Section~\ref{sec:oracleheuristics} shows how we
mitigate this fundamental limitation of Critical Slicing and
Section~\ref{sec:fault-misses} shows how problematic is that issue in
practice.

@@

The proof is based on the outlined argument that irrelevant
components $j$ have their ranks reduced as $\N{11}$ decreases and
$\N{01}$ increases. If those irrelevant components appear at positions
above the faulty component, it is possible that the faulty component
becomes more suspicious relative to $j$, \ie{}, the ranking of the
faulty component increases. If those components appear at positions
below the faulty components, the ranking of the faulty components is
unaffected.

\subsection{Oracle Heuristics}
\label{sec:oracleheuristics}

% \Mar{Sofia, I think this was way too low-level for intro and decided
%   to move here. please check how to fit.}
% \Fix{
% A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}. \morpho{} retrieves as an output the input for \lithium{}. \lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statements that resulted from the minimization. \morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}. }

The \cs{} technique is somewhat based on the \textit{statement deletion} mutant
operator of the mutation-based testing methodology. This operator was designed
based on the idea that each statement has an effect on the program output (i.e.,
oracle). Thus, testers are encouraged to design test sets that cause all
statements to be executed and generate outputs that are different from the
program under test.

Mozilla's Lithium takes as input a function of interest that can be designed
according to the problem to be solved. The function of interest determines if
the test case output is interesting or not. Our function simply compares the
failing test output with the output obtained when re-running again the failing
test after deleting the slice, as explained in Section~\ref{sec:slicing}. Thus,
if the initial test output is the same as the one after removing the slice
\{$c_2$,$c_5$\}, then the slice is removed. This means that the slice is not
necessary to reveal the fault because if removed the test output is still the
same. The output is extracted from the stacktrace obtained through the failing
test execution. The stacktrace provides information not only about the place
where the fault was revelead but also the path taken to get there. Thus, our
approach considers not only the exception caught by the failing test but also
the path that was taken to reveal the fault. The following provides an example:

\vspace{3mm}
\begin{myframe} \label{box:1}
junit.framework.AssertionFailedError, \\
at junit.framework.Assert.fail(Assert.java:55), \\
at junit.framework.Assert.assertTrue(Assert.java:22), \\
at junit.framework.Assert.assertFalse(Assert.java:39), \\
at junit.framework.Assert.assertFalse(Assert.java:47), \\
at junit.framework.TestCase.assertFalse(TestCase.java:219), \\
at org.jfree.chart.util.junit.ShapeUtilitiesTests.\\testEqualGeneralPaths(ShapeUtilitiesTests.java:212), \\
...
\end{myframe}

Considering some of the stacktrace information about the path taken to reveal
the fault solved the issue of generic oracles (e.g., NPE or generic
AssertionFailedError expections as the one presented before) mentioned in
Theorem~\ref{the:1}. There are faults whose outputs could slightly differ from
one execution to another. For example, exceptions including information of
memory addresses. For these cases, it was developed a mechanism to compare the
rest of the output ignoring the identifier of the memory address. This heuristic
also handles StackOverflow oracles.
%
\section{Evaluation}
\label{sec:eval}
%
To evaluate our approach, we compare the cost of diagnosing
a collection of faults using \sfl{} versus \comb{}.
%
\subsection{Objects of Analysis}\label{sec:analysis}

>>>>

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at {\footnotesize\url{https://github.com/MozillaSecurity/lithium}} (Accessed \today)}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in
number of lines---of chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed \today)}. Our implementation is publicly
available at \textit{$<$anonymized for double-blind review$>$}.

If test oracles are too general, it is possible, conceptually, that
the critical slicing algorithm produces slices without the faulty
code. Suppose that a test fails with a Null-Pointer Exception (NPE)
and the criterion used to slice the code in that case (\ie{}, the
oracle) is the presence of NPE in the output, regardless of the
location that raises that exception. It is therefore possible that the
slice obtained at some iteration of the aforementioned algorithm
raises NPE, but it does so in a different part of the code. If that
happens, the critical slicing algorithm would consider that as an
acceptable simplification--as it satisfied the criterion--and would
continue. As the algorithm does not backtrack, it would be impossible,
to obtain a slice containing the faulty component from that point
on.\hfill{\tiny$\blacksquare$}

It is worth noting that this is not a problem that afflicts only CS;
\emph{all} purely dynamic slicing techniques manifest this
problem~\cite{Lin:2018:BDE:3238147.3238163}. To mitigate the issue in
CS, it is necessary to make oracles more specific. For that, our
approach was to use as the slicing criterion the stack trace
associated with the test failure. That decision increases the chances
that the sliced program will follow a path to the error similar to
that followed by the original program. \Mar{Sofia, if you think it is
  necessary, explain if you needed to abstract something in the
  stacktrace. I did not understand that memory location thing.}

% \Mar{Sofia, I think this was way too low-level for intro and decided
%   to move here. please check how to fit.}
% \Fix{
% A couple of different tools were designed to perform this empirical study: \morpho{} and \lithium{}. \morpho{} retrieves as an output the input for \lithium{}. \lithium{} uses the input to reduce the search domain for \sfl{} and outputs the statmeents that resulted from the minimization. \morpho{} uses this to update the spectrum matrix, performs the before and after \sfl{} evaluation using the corresponding matrix, and outputs the metrics that report the \sfl{} performance for both cases ~---~ before and after using \ds{}. }

%---------------------------------------------------------
%% \subsubsection{\label{sec:oracleheuristics}Oracle Heuristics.}~

%% The \cs{} technique is somewhat based on the \textit{statement deletion} mutant
%% operator of the mutation-based testing methodology. This operator was designed
%% based on the idea that each statement has an effect on the program output (i.e.,
%% oracle). Thus, testers are encouraged to design test sets that cause all
%% statements to be executed and generate outputs that are different from the
%% program under test.

%% Mozilla's Lithium takes as input a function of interest that can be designed
%% according to the problem to be solved. The function of interest determines if
%% the test case output is interesting or not. Our function simply compares the
%% failing test output with the output obtained when re-running again the failing
%% test after deleting the slice, as explained in Section~\ref{sec:slicing}. Thus,
%% if the initial test output is the same as the one after removing the slice
%% \{$c_2$,$c_5$\}, then the slice is removed. This means that the slice is not
%% necessary to reveal the fault because if removed the test output is still the
%% same. The output is extracted from the stacktrace obtained through the failing
%% test execution. The stacktrace provides information not only about the place
%% where the fault was revelead but also the path taken to get there. Thus, our
%% approach considers not only the exception caught by the failing test but also
%% the path that was taken to reveal the fault. The following provides an example:

%% \vspace{3mm}
%% \begin{myframe} \label{box:1}
%% junit.framework.AssertionFailedError, \\
%% at junit.framework.Assert.fail(Assert.java:55), \\
%% at junit.framework.Assert.assertTrue(Assert.java:22), \\
%% at junit.framework.Assert.assertFalse(Assert.java:39), \\
%% at junit.framework.Assert.assertFalse(Assert.java:47), \\
%% at junit.framework.TestCase.assertFalse(TestCase.java:219), \\
%% at org.jfree.chart.util.junit.ShapeUtilitiesTests.\\testEqualGeneralPaths(ShapeUtilitiesTests.java:212), \\
%% ...
%% \end{myframe}

%% Considering some of the stacktrace information about the path taken to reveal
%% the fault solved the issue of generic oracles (e.g., NPE or generic
%% AssertionFailedError expections as the one presented before) mentioned in
%% Theorem~\ref{the:1}. There are faults whose outputs could slightly differ from
%% one execution to another. For example, exceptions including information of
%% memory addresses. For these cases, it was developed a mechanism to compare the
%% rest of the output ignoring the identifier of the memory address. This heuristic
%% also handles StackOverflow oracles.
%---------------------------------------------------------

@@

\begin{wrapfigure}[8]{1}{0.25\textwidth}
  \hspace{-2ex}
  \centering
  \scriptsize
  \setlength{\tabcolsep}{3.5pt}  
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}

@@

@@

The proof is based on the outlined argument that irrelevant
components $j$ have their ranks reduced as $\N{11}$ decreases and
$\N{01}$ increases. If those irrelevant components appear at positions
above the faulty component, it is possible that the faulty component
becomes more suspicious relative to $j$, \ie{}, the ranking of the
faulty component increases. If those components appear at positions
below the faulty components, the ranking of the faulty components is
unaffected.\hfill{\tiny$\blacksquare$}

%
\section{Evaluation}
\label{sec:eval}
%
To evaluate our approach, we compare the cost of diagnosing
a collection of faults using \sfl{} versus \comb{}.
%
\subsection{Objects of Analysis}\label{sec:analysis}
